Pollution, agricultural productivity, and development: Evidence from coal in plants in India^[All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution_development]

### 2023-01-14 draft/draft.Rmd
updated draft

# This includes latex arguments
header-includes:
  - \newcommand{\beginappendix}{   
      \setcounter{table}{0}  
      \renewcommand{\thetable}{A\arabic{table}} 
      \setcounter{figure}{0} 
      \renewcommand{\thefigure}{A\arabic{figure}}
    }  # Relabel appendix tables/figures as e.g. A1
  - \usepackage[capposition=top]{floatrow}
  - \usepackage{placeins}   # THis is for /FloatBarrier
  - \usepackage{setspace}
  - \usepackage{dcolumn}
  - \usepackage{booktabs}
  - \usepackage{siunitx}
  - \usepackage{amsmath}
  - \usepackage{enumerate}
  - \usepackage[shortlabels]{enumitem}
  - \usepackage[hang,flushmargin]{footmisc}		# no indents on footnotes
---

@@

# Tables
pollutiontable <- readRDS("pollution_development/draft/tables/pollutiontable.rds")
yieldtable <- readRDS("pollution_development/draft/tables/yieldtable.rds")
yieldtabletwo <- readRDS("pollution_development/draft/tables/yieldtabletwo.rds")
yieldtablehet <- readRDS("pollution_development/draft/tables/yieldtablehet.rds")
pmeffects <- readRDS("pollution_development/draft/tables/yieldtablePM.rds")
labortable <- readRDS("pollution_development/draft/tables/labortable.rds")
labortablemonsoon <- readRDS("pollution_development/draft/tables/labortablemonsoon.rds")
labortablewinter <- readRDS("pollution_development/draft/tables/labortablewinter.rds")
labortableold <- readRDS("pollution_development/draft/tables/labortableold.rds")
ntltable <- readRDS("pollution_development/draft/tables/ntltable.rds")
yieldtableleads <- readRDS("pollution_development/draft/tables/yieldtableleads.rds")
yieldtablepostplant <- readRDS("pollution_development/draft/tables/yieldtablepostplant.rds")
laborplot <- readRDS("pollution_development/draft/tables/laborplot.rds")

@@

@@

# Table
colnames(pollutiontable) <- c("(1)", "(2)", "(3)", "(4)")
kable(
      pollutiontable, caption = "Wind direction and particulate matter",
      align = "cccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           general = c(
                       "Note: Standard errors are in parentheses and are clustered at the village level.",
                       "* p<0.10 ** p<0.05 *** p<0.01"
                       ), 
           general_title = "",
           threeparttable = TRUE
           ) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(c(2:5),width = "2cm") %>%
  row_spec(c(3), bold = TRUE) %>%
  row_spec(6, hline_after = TRUE) %>%
  add_header_above(c(" ", "1998-2015" = 2, "2002-2013" = 2)) %>%
  kable_classic_2()

@@

# Table
colnames(yieldtable) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtable, caption = "Wind direction and agricultural productivity",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           general = c(
                       "Note: Standard errors are in parentheses and are clustered at the village level.",
                       "* p<0.10 ** p<0.05 *** p<0.01"
                       ), 
           general_title = "",
           threeparttable = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(5, bold = TRUE) %>%
  row_spec(9, hline_after = TRUE) %>%
  add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(yieldtabletwo) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtabletwo, caption = "Pollution and agricultural productivity, IV estimates",
      align = "cccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           general = c(
                       "Note: Standard errors are in parentheses and are clustered at the village level.",
                       "* p<0.10 ** p<0.05 *** p<0.01"
                       ), 
           general_title = "",
           threeparttable = TRUE
           ) %>%
  column_spec(1, width = "3.5cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(c(5,11), bold = TRUE) %>%
  row_spec(c(9:10), hline_after = TRUE) %>%
  add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(yieldtablehet) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtablehet, caption = "Heterogeneity in the effects of pollution on productivity",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           general = c(
                       "Note: Standard errors are in parentheses and are clustered at the village level.",
                       "* p<0.10 ** p<0.05 *** p<0.01"
                       ), 
           general_title = "",
           threeparttable = TRUE
           ) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(c(13), hline_after = TRUE) %>%
  row_spec(c(11), bold = TRUE) %>%
  add_header_above(c(" ", ">p(50)" = 1, "<=p(50)" = 1, "all" = 3)) %>%
  kable_classic_2()

@@

# Table
colnames(labortable) <- c("all", "all", "self", "wage", "farm", "non-farm")
kable(
      labortable, caption = "Wind direction and labor allocation",
      align = "cccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           general = c(
                       "Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education.",
                       "* p<0.10 ** p<0.05 *** p<0.01"
                       ), 
           general_title = "",
           threeparttable = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:7),width = "1.5cm") %>%
  row_spec(c(8), hline_after = TRUE) %>%
  row_spec(c(4,7), bold = TRUE) %>%
  kable_classic_2()

@@

# Table
labortableold <- labortableold[,-1]
colnames(labortableold) <- c("all", "self", "wage", "farm", "non-farm")
kable(
      labortableold, caption = "Wind direction and labor allocation, heterogeneity by age",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           general = c(
                       "Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education.",
                       "* p<0.10 ** p<0.05 *** p<0.01"
                       ), 
           general_title = "",
           threeparttable = TRUE
           ) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(c(2:6),width = "1.5cm") %>%
  row_spec(c(10), hline_after = TRUE) %>%
  row_spec(c(6,9), bold = TRUE) %>%
  kable_classic_2()

@@

# Table
colnames(ntltable) <- c("(1)", "(2)")
kable(
      ntltable, caption = "Wind direction and nightlight growth",
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           general = c(
                       "Note: Standard errors are in parentheses and are clustered at the village level.",
                       "* p<0.10 ** p<0.05 *** p<0.01"
                       ), 
           general_title = "",
           threeparttable = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  row_spec(c(9), hline_after = TRUE) %>%
  row_spec(c(5,8), bold = TRUE) %>%
  kable_classic_2()

@@

# Table
kable(
      data, caption = "Remote sensing data sources",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           general = c(
                       "Note: NCAR stands for the National Center for Atmospheric Research. Additional information on Global Energy Monitor and NCAR can be found on their websites, at https://globalenergymonitor.org/projects/global-coal-plant-tracker and https://climatedataguide.ucar.edu/, respectively."
                       ), 
           general_title = "",
           threeparttable = TRUE
           ) %>%
  column_spec(1, width = "2cm") %>%
  column_spec(2,width = "4.5cm") %>%
  column_spec(c(3:4),width = "3.5cm") %>%
  kable_styling(latex_options = "HOLD_position") %>%
  kable_classic_2()

@@

# Table
colnames(yieldtablepostplant) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtablepostplant, caption = "Wind direction and agricultural productivity, post-coal plant only",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           general = c(
                       "Note: Standard errors are in parentheses and are clustered at the village level. The sample is restricted to village-years after a coal plant was built near the village.",
                       "* p<0.10 ** p<0.05 *** p<0.01"
                       ), 
           general_title = "",
           threeparttable = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(5, bold = TRUE) %>%
  row_spec(9, hline_after = TRUE) %>%
  add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_styling(latex_options = "HOLD_position") %>%
  kable_classic_2()

@@

# Table
colnames(yieldtableleads) <- c("(1)", "(2)")
kable(
      yieldtableleads, caption = "Agricultural productivity and pollution leads",
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           general = c(
                       "Note: Standard errors are in parentheses and are clustered at the village level.",
                       "* p<0.10 ** p<0.05 *** p<0.01"
                       ), 
           general_title = "",
           threeparttable = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  row_spec(c(12), hline_after = TRUE) %>%
  row_spec(c(9), bold = TRUE) %>%
  kable_classic_2()

@@

# Table
colnames(labortablemonsoon) <- c("all", "all", "self", "wage", "farm", "non-farm")
kable(
      labortablemonsoon, caption = "Wind direction and labor allocation, monsoon season only",
      align = "cccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           general = c(
                       "Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education.",
                       "* p<0.10 ** p<0.05 *** p<0.01"
                       ), 
           general_title = "",
           threeparttable = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:7),width = "1.5cm") %>%
  row_spec(c(8), hline_after = TRUE) %>%
  row_spec(c(4,7), bold = TRUE) %>%
  kable_classic_2()

@@

# Table
colnames(labortablewinter) <- c("all", "all", "self", "wage", "farm", "non-farm")
kable(
      labortablewinter, caption = "Wind direction and labor allocation, winter season only",
      align = "cccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           general = c(
                       "Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education.",
                       "* p<0.10 ** p<0.05 *** p<0.01"
                       ), 
           general_title = "",
           threeparttable = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:7),width = "1.5cm") %>%
  row_spec(c(8), hline_after = TRUE) %>%
  row_spec(c(4,7), bold = TRUE) %>%
  kable_classic_2()

>>>>

# This includes latex arguments
header-includes:
  - \newcommand{\beginappendix}{   
      \setcounter{table}{0}  
      \renewcommand{\thetable}{A\arabic{table}} 
      \setcounter{figure}{0} 
      \renewcommand{\thefigure}{A\arabic{figure}}
    }  # Relabel appendix tables/figures as e.g. A1
  - \usepackage[capposition=top]{floatrow}
  - \usepackage{placeins}   # THis is for /FloatBarrier
  - \usepackage{setspace}
  - \usepackage{dcolumn}
  - \usepackage{booktabs}
  - \usepackage{siunitx}
  - \usepackage{amsmath}
  - \usepackage{enumerate}
  - \usepackage[shortlabels]{enumitem}
  - \usepackage[hang,flushmargin]{footmisc}		# no indents on footnotes
  - \usepackage{makecell}
---

@@

# Tables
plantresultstable <- readRDS("pollution_development/draft/tables/plantresultstable.rds")
pollutiontable <- readRDS("pollution_development/draft/tables/pollutiontable.rds")
yieldtable <- readRDS("pollution_development/draft/tables/yieldtable.rds")
yieldtabletwo <- readRDS("pollution_development/draft/tables/yieldtabletwo.rds")
yieldtablehet <- readRDS("pollution_development/draft/tables/yieldtablehet.rds")
pmeffects <- readRDS("pollution_development/draft/tables/yieldtablePM.rds")
labortable <- readRDS("pollution_development/draft/tables/labortable.rds")
labortablemonsoon <- readRDS("pollution_development/draft/tables/labortablemonsoon.rds")
labortablewinter <- readRDS("pollution_development/draft/tables/labortablewinter.rds")
labortableold <- readRDS("pollution_development/draft/tables/labortableold.rds")
ntltable <- readRDS("pollution_development/draft/tables/ntltable.rds")
yieldtableleads <- readRDS("pollution_development/draft/tables/yieldtableleads.rds")
yieldtablepostplant <- readRDS("pollution_development/draft/tables/yieldtablepostplant.rds")
laborplot <- readRDS("pollution_development/draft/tables/laborplot.rds")

@@

## Where do coal plants open?

A large question looms with respect to identification: what are the characteristics of areas near the construction of new coal plants? While I examine the identifying assumptions in a panel context below, I begin with this static question here. Table \@ref(tab:plantresultstable) presents four separate regressions. The first two columns use 1991 census data -- downloaded from SHRUG -- and the second two columns use 2001 census data, all at the village level. The first column presents results from regressing a dummy for whether there is a coal plant within 30km in 1991 on several census variables. Villages with higher populations and higher literacy in 1991 are more likely to be near a coal plant at the time. Interestingly, however, they are less likely to have a paved road.

```{r plantresultstable, include = TRUE, echo = FALSE, message = FALSE, warning = FALSE}

# Table
colnames(plantresultstable) <- c("1991", "2001", "2001", "2011")
kable(
      plantresultstable, caption = "Local characteristics and the construction of coal plants",
      align = "cccc", booktabs = TRUE, linesep = "", escape = FALSE
      ) %>%
  footnote(
           "Note: Robust standard errors are in parentheses. The outcome in the first column is whether the village is within 30km of a coal plant in 1991. The second column is whether a village in 1991 will have a coal plant in 2001, conditional on not having one in 1991. The last two columns are similarly defined, except using 2001 and 2011 as the years. * p<0.10 ** p<0.05 *** p<0.01",
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE,
           escape = FALSE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:5),width = "2cm") %>%
  row_spec(9, hline_after = TRUE) %>%
  add_header_above(c(" ", "1991 census" = 2, "2001 census" = 2)) %>%
  kable_classic_2()

The second column keeps the 1991 census data but changes the outcome variable to a dummy for whether there *will be* a coal plant constructed before 2001. This column restricts the sample to only villages that do not already have a coal plant in 1991. Population is no longer a significant predictor while the coefficients on literacy and the presence of a paved road have flipped.

The last two columns are particularly relevant to the current results. They present similar results to those in the first two columns, but use the 2001 census data and a dummy for the presence of a coal plant in 2001 and 2011 in columns three and four, respectively. Importantly, I include agricultural productivity in the monsoon season of 2002 -- the earliest year available -- as an additional predictor. In 2001, agricultural productivity is a strong predictor for the presence of a coal plant. Moreover, it is also a significant predictor of the construction of a coal plant between 2001 and 2011 (column four). Given that the coefficient is positive, this indicates that coal plants are more likely to be built in areas with higher agricultural productivity. In other words, any selection in the overall location of coal plants would bias against finding negative effects of pollution on agricultural productivity.

However, note that this is not the same as looking at wind direction. I discuss this more in the results section below.

@@

# Table
colnames(pollutiontable) <- c("(1)", "(2)", "(3)", "(4)")
kable(
      pollutiontable, caption = "Wind direction and particulate matter",
      align = "cccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(c(2:5),width = "2cm") %>%
  row_spec(c(3), bold = TRUE) %>%
  row_spec(6, hline_after = TRUE) %>%
  add_header_above(c(" ", "1998-2015" = 2, "2002-2013" = 2)) %>%
  kable_classic_2()

@@

# Table
colnames(yieldtable) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtable, caption = "Wind direction and agricultural productivity",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(5, bold = TRUE) %>%
  row_spec(9, hline_after = TRUE) %>%
  add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(yieldtabletwo) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtabletwo, caption = "Pollution and agricultural productivity, IV estimates",
      align = "cccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3.5cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(c(5,11), bold = TRUE) %>%
  row_spec(c(9:10), hline_after = TRUE) %>%
  add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(yieldtablehet) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtablehet, caption = "Heterogeneity in the effects of pollution on productivity",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(c(13), hline_after = TRUE) %>%
  row_spec(c(11), bold = TRUE) %>%
  add_header_above(c(" ", ">p(50)" = 1, "<=p(50)" = 1, "all" = 3)) %>%
  kable_classic_2()

@@

# Table
colnames(labortable) <- c("all", "all", "self", "wage", "farm", "non-farm")
kable(
      labortable, caption = "Wind direction and labor allocation",
      align = "cccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:7),width = "1.5cm") %>%
  row_spec(c(8), hline_after = TRUE) %>%
  row_spec(c(4,7), bold = TRUE) %>%
  kable_classic_2()

@@

# Table
labortableold <- labortableold[,-1]
colnames(labortableold) <- c("all", "self", "wage", "farm", "non-farm")
kable(
      labortableold, caption = "Wind direction and labor allocation, heterogeneity by age",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(c(2:6),width = "1.5cm") %>%
  row_spec(c(10), hline_after = TRUE) %>%
  row_spec(c(6,9), bold = TRUE) %>%
  kable_classic_2()

@@

# Table
colnames(ntltable) <- c("(1)", "(2)")
kable(
      ntltable, caption = "Wind direction and nightlight growth",
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  row_spec(c(9), hline_after = TRUE) %>%
  row_spec(c(5,8), bold = TRUE) %>%
  kable_classic_2()

@@

# Table
kable(
      data, caption = "Remote sensing data sources",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: NCAR stands for the National Center for Atmospheric Research. Additional information on Global Energy Monitor and NCAR can be found on their websites, at https://globalenergymonitor.org/projects/global-coal-plant-tracker and https://climatedataguide.ucar.edu/, respectively.", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "2cm") %>%
  column_spec(2,width = "4.5cm") %>%
  column_spec(c(3:4),width = "3.5cm") %>%
  kable_styling(latex_options = "HOLD_position") %>%
  kable_classic_2()

@@

# Table
colnames(yieldtablepostplant) <- c("(1)", "(2)", "(3)", "(4)", "(5)")
kable(
      yieldtablepostplant, caption = "Wind direction and agricultural productivity, post-coal plant only",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The sample is restricted to village-years after a coal plant was built near the village. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:6),width = "2cm") %>%
  row_spec(5, bold = TRUE) %>%
  row_spec(9, hline_after = TRUE) %>%
  add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_styling(latex_options = "HOLD_position") %>%
  kable_classic_2()

@@

# Table
colnames(yieldtableleads) <- c("(1)", "(2)")
kable(
      yieldtableleads, caption = "Agricultural productivity and pollution leads",
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  row_spec(c(12), hline_after = TRUE) %>%
  row_spec(c(9), bold = TRUE) %>%
  kable_classic_2()

@@

# Table
colnames(labortablemonsoon) <- c("all", "all", "self", "wage", "farm", "non-farm")
kable(
      labortablemonsoon, caption = "Wind direction and labor allocation, monsoon season only",
      align = "cccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:7),width = "1.5cm") %>%
  row_spec(c(8), hline_after = TRUE) %>%
  row_spec(c(4,7), bold = TRUE) %>%
  kable_classic_2()

@@

# Table
colnames(labortablewinter) <- c("all", "all", "self", "wage", "farm", "non-farm")
kable(
      labortablewinter, caption = "Wind direction and labor allocation, winter season only",
      align = "cccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:7),width = "1.5cm") %>%
  row_spec(c(8), hline_after = TRUE) %>%
  row_spec(c(4,7), bold = TRUE) %>%
  kable_classic_2()
